Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-21 cordillera-cycle.tex
Rev. Jarosch: add refs to clarify new outline.

      Our palaeo-climate forcing therefore includes spatial temperature and
      precipitation grids derived from a~present-day atmospheric reanalysis
      \citep{Mesinger.etal.2006} that includes the steep precipitation
      gradients previously identified as necessary to model the LGM extent
      of the Cordilleran ice sheet in agreement with its geological imprint
      \citep{Seguinot.etal.2014}. To mimic climate evolution through the
      last glacial cycle, these grids are simply supplemented by lapse-rate
      corrections and temperature offset time series. The latter are
      obtained by scaling six different palaeo-temperature reconstructions
      from proxy records around the globe, including two oxygen isotope
      records from Greenland ice cores \citep{Dansgaard.etal.1993,
      Andersen.etal.2004}, two oxygen isotope records from Antarctic ice
      cores \citep{Petit.etal.1999,Jouzel.etal.2007}, and two alkenone
      unsaturation index records from Northwest Pacific ocean sediment cores
      \citep{Herbert.etal.2001}. After testing the model sensitivity to
      these climate forcing time-series and to some of the most influential
      ice flow parameters, we then proceed to compare the model output
      to geological evidence and discuss the timing and extent of glaciation
      and the patterns of deglaciation, based on which we use the
      applicability of different records to modelling the history of the
      Cordilleran ice sheet.

@@

      Basal topography is derived from the ETOPO1 combined topography and
      bathymetry dataset with a~resolution of 1\,arc-min
      \citep{Amante.Eakins.2009}. Sea level is lowered as a~function of time
      based on the Spectral Mapping Project
      \citep[SPECMAP,][]{Imbrie.etal.1989} time scale. Geothermal heat flux
      is applied as a~constant value of 70\,\unit{mW\,m^{-2}} at
      3\,\unit{km} depth (Sect.~\ref{sec:icedyn}). Basal sliding follows
      a pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Ice shelf calving is calculated based on ice thickness and principle
      strain rates (Sect.~\ref{sec:sliding}). Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Default parameter values are given in
      Table~\ref{tab:params}. Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbated
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}).

>>>>

      Our palaeo-climate forcing therefore includes spatial temperature and
      precipitation grids derived from a~present-day atmospheric reanalysis
      \citep{Mesinger.etal.2006} that includes the steep precipitation
      gradients previously identified as necessary to model the LGM extent
      of the Cordilleran ice sheet in agreement with its geological imprint
      \citep{Seguinot.etal.2014}. To mimic climate evolution through the
      last glacial cycle, these grids are simply supplemented by lapse-rate
      corrections and temperature offset time series. The latter are
      obtained by scaling six different palaeo-temperature reconstructions
      from proxy records around the globe, including two oxygen isotope
      records from Greenland ice cores \citep{Dansgaard.etal.1993,
      Andersen.etal.2004}, two oxygen isotope records from Antarctic ice
      cores \citep{Petit.etal.1999,Jouzel.etal.2007}, and two alkenone
      unsaturation index records from Northwest Pacific ocean sediment cores
      \citep{Herbert.etal.2001}. After testing the model sensitivity to
      these climate forcing time-series (Sect.~\ref{sec:results}) and to
      some of the most influential ice flow parameters
      (Sect.~\ref{sec:sens}), we then proceed to compare the model output
      to geological evidence and discuss the timing and extent of glaciation
      and the patterns of deglaciation, based on which we use the
      applicability of different records to modelling the history of the
      Cordilleran ice sheet (Sect.~\ref{sec:discussion}).

@@

      Basal topography is derived from the ETOPO1 combined topography and
      bathymetry dataset with a~resolution of 1\,arc-min
      \citep{Amante.Eakins.2009}. Sea level is lowered as a~function of time
      based on the Spectral Mapping Project
      \citep[SPECMAP,][]{Imbrie.etal.1989} time scale. Geothermal heat flux
      is applied as a~constant value of 70\,\unit{mW\,m^{-2}} at
      3\,\unit{km} depth (Sect.~\ref{sec:icedyn}). Basal sliding follows
      a pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Ice shelf calving is calculated based on ice thickness and principle
      strain rates (Sect.~\ref{sec:sliding}). Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Default parameter values are given in
      Table~\ref{tab:params}. Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbated
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}). A sensitivity study
      to some of the most influential ice rheology (Sect~\ref{sec:icedyn})
      and basal sliding (Sect.~\ref{sec:sliding}) parameters was performed
      (Table~\ref{tab:sens_params}).
